A pipeline to analyse time-course gene expression data

### 2020-07-10 scripts/manuscript.Rmd
update

 `moanin` is available from GitHub, and can be installed using the `install_github` function in the package `devtools`:

```{r eval=FALSE}
library(devtools)
install_github("NelleV/moanin")
library(moanin)
```

@@

```{r all_libraries}
# From github
library(timecoursedata)

@@

# From Bioconductor
library(topGO)
library(biomaRt)
library(KEGGprofile)
library(BiocWorkflowTools)

# From GitHub
library(moanin)
```

@@

```{r}
# Now load in the metadata
data(shoemaker2015)
meta = shoemaker2015$meta
data = shoemaker2015$data
```

>>>>

 `moanin` is available from GitHub, and can be installed using the `install_github` function in the package `devtools`, along with the corresponding package that contains time course datasets we will use:

```{r eval=FALSE}
library(devtools)
install_github("NelleV/moanin")
install_github("NelleV/timecoursedata")
```

@@

```{r all_libraries}
# From Github
library(moanin)
library(timecoursedata)

@@

# From Bioconductor
library(topGO)
library(biomaRt)
library(KEGGprofile)
library(BiocWorkflowTools) #Needed for compiling the .Rmd script
```

If Bioconductor is installed, the CRAN and Bioconductor packages above can be installed via

```{r eval=FALSE}
BiocManager::install(c("NMF","ggfortify","topGO","biomaRt","KEGGprofile","BiocWorkflowTools"))
```

@@

```{r loadData}
# Now load in the metadata
data(shoemaker2015)
meta = shoemaker2015$meta
data = shoemaker2015$data
```
